Staged Abstract Interpreters

### 2019-09-11 paper/20_prelim.tex
polish
typo

\paragraph{Basic Types} We start with some basic type definitions that are used
in the interpreter. The identifiers in the program are represented by strings.
To represent states, two required components for the interpreter are
environments, represented by type @Env@, and stores, represented by type
@Store@. An @Env@ maps identifiers to addresses, and a @Store@ maps addresses to
values. An environment captures bound variables in the scope of current control, and
@Store@ models a persistent heap through the program run-time.  Currently,
the domains of addresses and values are still abstract; hence, they are
declared as abstract types.
\begin{lstlisting}
  trait Semantics {
    type Ident = String; type Addr; type Value
    type Env = Map[Ident, Addr]; type Store = Map[Addr, Value]
    type R[_] // Binding-time as a higher-kinded type
    ... // The definitions in the rest of this section are enclosed in trait Semantics.
  }
\end{lstlisting}

@@

\paragraph{The Interpreter} We can now construct the semantics-agnostic interpreter
in monadic form, shown in Figure \ref{fig:shared_int}. The basic idea
of generic interpretation is to traverse the abstract syntax tree
while maintaining the effects (such as environment and state updates).
Note that the interpreter is written in open-recursive style: it cannot
refer to itself directly. Instead, @eval@ takes an additional parameter @ev@ of
type @Expr => Ans@ that refers to itself. Consequently, the method @close@ that
lifts lambda terms to closures and method @ap_clo@ that applies functions also
takes an extra @ev@, because evaluations may happen inside them.
To close the open recursion, we use a fixed-point operator @fix@.
For concrete-interpretation instantiation, @fix@ works like the Y combinator;
for abstract-interpretation instantiation, it will instrument the interpreter
by memoizing @ev@'s inputs and outputs, which ensures the termination of
abstract interpretation.
Finally, there is a top-level wrapper @run@. The return type @Result@
depends on the kind of monads being used and is therefore also left abstract.
\begin{lstlisting}
  def fix(ev: (Expr => Ans) => (Expr => Ans)): Expr => Ans
  type Result; def run(e: Expr): Result
\end{lstlisting}

>>>>

\paragraph{Basic Types} We start with some basic type definitions that are used
in the interpreter. The identifiers in the program are represented by strings.
To represent states, two required components for the interpreter are
environments, represented by type @Env@, and stores, represented by type
@Store@. An @Env@ maps identifiers to addresses, and a @Store@ maps addresses to
values. An environment captures bound variables in the scope of current control, and
a store models a persistent heap through the program run-time.  Currently,
the domains of addresses and values are still abstract; hence, they are
declared as abstract types.
\begin{lstlisting}
  trait Semantics {
    type Ident = String; type Addr; type Value
    type Env = Map[Ident, Addr]; type Store = Map[Addr, Value]
    type R[_] // Binding-time as a higher-kinded type
    ... // The definitions in the rest of this section are enclosed in trait Semantics.
  }
\end{lstlisting}

@@

\paragraph{The Interpreter} We can now construct the semantics-agnostic interpreter
in monadic form, as shown in Figure \ref{fig:shared_int}. The basic idea
of generic interpretation is to traverse the abstract syntax tree
while maintaining the effects (such as environment and state updates).
Note that the interpreter is written in open-recursive style: it cannot
refer to itself directly. Instead, @eval@ takes an additional parameter @ev@ of
type @Expr => Ans@ that refers to itself. Consequently, the method @close@ that
lifts lambda terms to closures and method @ap_clo@ that applies functions also
takes an extra @ev@, because evaluations may happen inside them.
To close the open recursion, we use a fixed-point operator @fix@.
For concrete-interpretation instantiation, @fix@ works like the Y combinator;
for abstract-interpretation instantiation, it will instrument the interpreter
by memoizing @ev@'s inputs and outputs, which ensures the termination of
abstract interpretation.
Finally, there is a top-level wrapper @run@. The return type @Result@
depends on the kind of monads being used and is therefore also left abstract.
\begin{lstlisting}
  def fix(ev: (Expr => Ans) => (Expr => Ans)): Expr => Ans
  type Result; def run(e: Expr): Result
\end{lstlisting}
